Add Code

### 2025-02-12 choose_license.qmd
Fix location of footnotes
Place them after any punctuation

One solution is to make such a work simultaneously available
under two (or more) licenses, at the choice of the recipient:
Either under a specified software license,
or under a Creative Commons license[^media].
This is called multi-licensing and makes it easier
to reuse both the rendered document as well as the code.
For example, one could write:

>>>>

One solution is to make such a work simultaneously available
under two (or more) licenses, at the choice of the recipient:
Either under a specified software license,
or under a Creative Commons license.[^media]
This is called multi-licensing and makes it easier
to reuse both the rendered document as well as the code.
For example, one could write:

### 2025-02-12 code.qmd
Fix location of footnotes
Place them after any punctuation

In practice, you would identify all pieces of software the project relies on.
A few of them are obvious, such as R itself, Quarto,
and the $\TeX$ distribution we installed before.
Then there are the individual R packages[^renv-copying],
Quarto extensions, and $\TeX$ packages.
All of them, in turn, may have dependencies
and it is up to you decide when not to dig deeper.
For example, some R packages are only thin wrappers around other R packages
or around system dependencies which also might deserve credit.
A system dependency is additional software
that you require on your computer apart from the R package.

@@

- __Think twice about your dependencies.__
  Every dependency increases the risk of irreproducibility in the future.
  Prefer packages that are well-maintained and light on dependencies[^pkg-deps].
  We also recommend you to read "When should you take a dependency?"
  by @Wickham2023PackagesDependency.

>>>>

In practice, you would identify all pieces of software the project relies on.
A few of them are obvious, such as R itself, Quarto,
and the $\TeX$ distribution we installed before.
Then there are the individual R packages,[^renv-copying]
Quarto extensions, and $\TeX$ packages.
All of them, in turn, may have dependencies
and it is up to you decide when not to dig deeper.
For example, some R packages are only thin wrappers around other R packages
or around system dependencies which also might deserve credit.
A system dependency is additional software
that you require on your computer apart from the R package.

@@

- __Think twice about your dependencies.__
  Every dependency increases the risk of irreproducibility in the future.
  Prefer packages that are well-maintained and light on dependencies.[^pkg-deps]
  We also recommend you to read "When should you take a dependency?"
  by @Wickham2023PackagesDependency.
